Enhanced Global PTM Discovery (G-PTM-D) with MetaMorpheus

### 2017-11-29 paper.tex
dfjkdjf

\title[Enhanced Global PTM Discovery (G-PTM-D) with MetaMorpheus]
  {Enhanced Global PTM Discovery (G-PTM-D) with MetaMorpheus}

>>>>

\title{Enhanced Global PTM Discovery (G-PTM-D) with MetaMorpheus}

\keywords{G-PTM-D, post-translational modification discovery, proteomics, database search, calibration, co-isolation, post-translational modification}
